\documentclass[12pt, twoside, a4paper, titlepage]{article}

\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}

% set the default code style
\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    basicstyle=\ttfamily\scriptsize,    
    numbers=left, % display line numbers on the left
    commentstyle=\color{green}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    identifierstyle=\color{red}
}

\begin{document}

\title{Embedded Systems \linebreak Final project report -- DB40, a.k.a. Freddie }
\author{Prasant Adhikari (pa1038), Jovan Jovancevic (jj1652)}
\maketitle

\section{Summary}
Over the past 7 weeks, we worked with an Arduino DSRobot -- a rudimentary 4-wheeled robotic car with a simple on-board webcam, produced by Kuman. The robot is capable of accepting controls over WiFi: go forward, stop turn, pan/tilt the camera and set motor speed. Further, the robot can provide the live feed from the camera, also through WiFi. In this report, we provide a detailed description of the solution we designed and implemented to address the 3 challenges we were given: 1) Go-to goal, 2) Leader-follower and 3) Trajectory tracking. Our system works on an out-of-the-box robot and does not require an external localizer. The controls code is written in C++ and image processing is done in Python, relying on OpenCV 3. It is robust to different lighting scene conditions and can be calibrated for any color tracking. On the downside, a scene that contains the color the robot is tracking can confuse the robot. Another system flaw is that the camera has to be manually adjusted for different tasks.

\section{Solution overview}



\section{Image processing}

\section{Controls}

\section{Results}

\end{document}